---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# paintingr

<!-- badges: start -->

<!-- badges: end -->

> "The greatest value of a picture is when it forces us to notice what we never expected to see." - John Tukey

Color is one of the most important attributes of a figure. Dedicated choice of color can help us deliver our idea more vividly.

------------------------------------------------------------------------

The goal of `paintingr` is to provide a set of palettes from paintings.

Structure of the package was based on coding from the [wesanderson](https://github.com/karthik/wesanderson) packages.

Some palettes derived from [三三两两的色盘](https://www.xiaohongshu.com/user/profile/5b5f7d724eacab10606aa72a?xhsshare=CopyLink&appuid=5af1b353f7e8b957de93044a&apptime=1647258634) .

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("thereallda/paintingr")
```

## Usage

```{r }
library(paintingr)
# display all palettes
display_all_palettes()
```

## Palettes

```{r, include=FALSE}
library(imager)
```

### Pearlgirl

Girl with a Pearl Earring - Johannes Vermeer (1665), [Source](https://www.mauritshuis.nl/en/our-collection/artworks/670-girl-with-a-pearl-earring/)

```{r, eval=FALSE}
paint_palette("Pearlgirl")
```

```{r, echo=FALSE}
paint <- load.image("img/Girl_with_a_Pearl_Earring.jpg")
par(mai=rep(0,4))
layout(matrix(c(1,1,2,2),byrow = TRUE), heights=c(6,1))
plot(paint,axes=FALSE,xlab="",ylab="")
paint_palette("Pearlgirl")
```

### Splash

A Bigger Splash - David Hockney (1967), [Source](https://www.tate.org.uk/art/artworks/hockney-a-bigger-splash-t03254)

```{r, eval=FALSE}
paint_palette("Splash")
```

```{r, echo=FALSE}
paint <- load.image("img/A_Bigger_Splash_David_Hockney.jpg")
par(mai=rep(0,4))
layout(matrix(c(1,1,2,2),byrow = TRUE), heights=c(6,1))
plot(paint,axes=FALSE,xlab="",ylab="")
paint_palette("Splash")
```

### Autumn

Autumn at Oirase - Kawase Hasui (1933), [Source](https://www.pepperholm.com/products/autumn-at-oirase)

```{r, eval=FALSE}
paint_palette("Autumn")
```

```{r, echo=FALSE}
paint <- load.image("img/autumn-at-oirase.jpg")
par(mai=rep(0,4))
layout(matrix(c(1,1,2,2),byrow = TRUE), heights=c(6,1))
plot(paint,axes=FALSE,xlab="",ylab="")
paint_palette("Autumn")
```

### Villeneuve

Matin à Villeneuve - Henri Biva (1905), [Source](https://en.wikipedia.org/wiki/Matin_%C3%A0_Villeneuve)

```{r, eval=FALSE}
paint_palette("Villeneuve")
```

```{r, echo=FALSE}
paint <- load.image("img/Villeneuve.jpeg")
par(mai=rep(0,4))
layout(matrix(c(1,1,2,2),byrow = TRUE), heights=c(6,1))
plot(paint,axes=FALSE,xlab="",ylab="")
paint_palette("Villeneuve")
```

### Ophelia

Ophelia - John Everett Millais (1851-1852), [Source](https://www.tate.org.uk/art/artworks/millais-ophelia-n01506)

```{r, eval=FALSE}
paint_palette("Ophelia")
```

```{r, echo=FALSE}
paint <- load.image("img/John_Everett_Millais-Ophelia.jpg")
par(mai=rep(0,4))
layout(matrix(c(1,1,2,2),byrow = TRUE), heights=c(6,1))
plot(paint,axes=FALSE,xlab="",ylab="")
paint_palette("Ophelia")
```

### Kitchen

Kitchen (Detail 2) - Liza Lou (1991–1996), [Source](https://whitney.org/collection/works/34855)

```{r, eval=FALSE}
paint_palette("Kitchen")
```

```{r, echo=FALSE}
paint <- load.image("img/kitchendetail2.jpeg")
par(mai=rep(0,4))
layout(matrix(c(1,1,2,2),byrow = TRUE), heights=c(6,1))
plot(paint,axes=FALSE,xlab="",ylab="")
paint_palette("Kitchen")
```

### Spring

SPRING BY THE SEINE - Claude Monet (1875), [Source](https://www.mcgawgraphics.com/products/claude-monet-spring-by-the-seine-1875)

```{r, eval=FALSE}
paint_palette("Spring")
```

```{r, echo=FALSE}
paint <- load.image("img/spring-by-the-seine-oscar-claude-monet.jpg")
par(mai=rep(0,4))
layout(matrix(c(1,1,2,2),byrow = TRUE), heights=c(6,1))
plot(paint,axes=FALSE,xlab="",ylab="")
paint_palette("Spring")
```

### Strawberries

Strawberries - Édouard Manet (1882), [Source](https://www.metmuseum.org/art/collection/search/436963)

```{r, eval=FALSE}
paint_palette("Strawberries")
```

```{r, echo=FALSE}
paint <- load.image("img/Strawberries_Edouard_Manet.jpg")
par(mai=rep(0,4))
layout(matrix(c(1,1,2,2),byrow = TRUE), heights=c(6,1))
plot(paint,axes=FALSE,xlab="",ylab="")
paint_palette("Strawberries")
```

### Seascape

Seascape at Saintes-Maries - Vincent van Gogh (1888), [Source](https://en.wikipedia.org/wiki/Saintes-Maries_(Van_Gogh_series))

```{r, eval=FALSE}
paint_palette("Seascape")
```

```{r, echo=FALSE}
paint <- load.image("img/Seascape_at_Saintes-Maries.jpg")
par(mai=rep(0,4))
layout(matrix(c(1,1,2,2),byrow = TRUE), heights=c(6,1))
plot(paint,axes=FALSE,xlab="",ylab="")
paint_palette("Seascape")
```

### Twilight

Twilight, Venice - Claude Monet (1908), [Source](https://commons.wikimedia.org/wiki/File:Claude_Monet_-_Twilight,_Venice.jpg)

```{r, eval=FALSE}
paint_palette("Twilight")
```

```{r, echo=FALSE}
paint <- load.image("img/Venice_Twilight.jpg")
par(mai=rep(0,4))
layout(matrix(c(1,1,2,2),byrow = TRUE), heights=c(6,1))
plot(paint,axes=FALSE,xlab="",ylab="")
paint_palette("Twilight")
```

### Abstract

Abstract Composition - Jessica Dismorr (1915), [Source](https://www.tate.org.uk/art/artworks/dismorr-abstract-composition-t01084)

```{r, eval=FALSE}
paint_palette("Abstract")
```

```{r, echo=FALSE}
paint <- load.image("img/T01084_10.jpg")
par(mai=rep(0,4))
layout(matrix(c(1,1,2,2),byrow = TRUE), heights=c(6,1))
plot(paint,axes=FALSE,xlab="",ylab="")
paint_palette("Abstract")
```

### Vesuivus

Vesuvius in Eruption - Joseph Wright of Derby (1776-1780), [Source](https://www.bl.uk/collection-items/vesuvius-in-eruption)

```{r, eval=FALSE}
paint_palette("Vesuvius")
```

```{r, echo=FALSE}
paint <- load.image("img/Vesuvius_in_Eruption.jpg")
par(mai=rep(0,4))
layout(matrix(c(1,1,2,2),byrow = TRUE), heights=c(6,1))
plot(paint,axes=FALSE,xlab="",ylab="")
paint_palette("Vesuvius")
```


## Examples

`ggplot2`-based examples

### Heatmap

Use `type="continuous"` to automatically interpolate between colors if you want more colors than the palette can offer (n \> 5/6).

```{r, warning=FALSE}
library(ggplot2)
# Dummy data
x <- LETTERS[1:20]
y <- paste0("var", seq(1,20))
data <- expand.grid(X=x, Y=y)
data$Z <- seq(1,20)+runif(400, 0, 5)

# Heatmap 
pal <- paint_palette("Autumn", n=100, type="continuous")
ggplot(data, aes(X, Y, fill= Z)) + 
  geom_tile() + 
  scale_fill_gradientn(colours = pal) + 
  scale_x_discrete(expand = c(0, 0)) +
  scale_y_discrete(expand = c(0, 0)) + 
  coord_equal() 
```

```{r}
# Heatmap with palette of "Vesuvius" 
pal2 <- paint_palette("Vesuvius", n=100, type="continuous")
ggplot(data, aes(X, Y, fill= Z)) + 
  geom_tile() + 
  scale_fill_gradientn(colours = pal2) + 
  scale_x_discrete(expand = c(0, 0)) +
  scale_y_discrete(expand = c(0, 0)) + 
  coord_equal() 
```

### Boxplot

```{r}
# use iris data from `ggplot2` for demonstration
data(iris)

ggplot(iris, aes(Species, Sepal.Length)) +
  geom_boxplot(aes(fill = Species)) +
  theme_classic() +
  theme(legend.position = "top") +
  scale_fill_manual(values = paint_palette("Villeneuve"))
```

### Scatter

```{r}
# Scatter
ggplot(iris, aes(Sepal.Length, Sepal.Width)) +
  geom_point(aes(color = Species)) +
  theme_classic() +
  theme(legend.position = "top") +
  scale_color_manual(values = paint_palette("Kitchen"))
```

### Violin plot

```{r}
data(mpg)
# violin plot with 7 colors, Spring palette only have six colors add one more
ggplot(mpg, aes(x=class, y=hwy, fill=class)) + 
  geom_violin() +
  theme_classic() +
  scale_fill_manual(values = c(paint_palette("Spring", n=6), "black"))
```

### Barplot

```{r}
ggplot(mpg, aes(x = class, fill = drv)) + 
  geom_bar() +
  theme_classic() +
  scale_fill_manual(values = paint_palette("Ophelia"))
```
